\chapter{The Mathematics of Gauge Theory\label{ch:gauge}}

	Gauge theory will play a central role in understanding the geometric Langlands correspondence physically. The role of the group $G$ in the Langlands correspondence is played by the gauge group in the physical theory. 

	\section{Fiber Bundles}
	\subsection{Definitions and Examples} % (fold)
	\label{sub:definitions_and_examples}
	
	% subsection definitions_and_examples (end)
	
		We will be working on a manifold $M$ (not necessarily Riemannian). In the first definition, we can assume $M$ is just a topological space. 
	\begin{defn}[Fiber Bundle]
		We define a \textbf{fiber bundle} $E$ on a topological space $M$ to be
		\begin{itemize}
			\item A topological space $E$ called the \textbf{total space}
			\item A topological space $M$ called the \textbf{base space}
			\item A topological space $F$ called the \textbf{fiber} 
			\item A \textbf{projection map} $\pi: E \to M$ that is surjective so that $\pi^{-1}(p) := E_p$ is homeomorphic to $F$. This is \textbf{the fiber over $p$}.
			\item For each $x \in E$ there is an open neighborhood $U \subseteq M$ of $p = \pi(x)$ so that there is a homeomorphism $\psi$ from $U \times F$ to $\pi^{-1}(U)$ in such a way that projection $p_1$ onto the first factor of $U \times F$ gives $\pi$
			\[
			\begin{tikzcd}
				U \times F \arrow[rd,swap,"p_1"] \arrow[rr,"\psi"] && \pi^{-1}(U) \arrow[dl,"\pi"]\\
				& U &
			\end{tikzcd}
			\]
		\end{itemize}
	\end{defn}
	Fiber bundles generalize the notion of cartesian products of two spaces $M$ and $F$ by allowing for the same local product structure but much more interesting global ``twisted structure''. 
	
	
	In physics, especially when calculations are to be performed, manifolds are often described in terms of a set of coordinate charts $U_\alpha$ that are homeomorphic to $\mathbb R^n$ with $n = \dim M$ and $\alpha \in I$ is an index in some indexing set, not necessarily finite\footnote{But in the case of $M$ compact, $I$ can always be made finite.}. A covering of $M$ in terms of coordinate charts 
	\[
		M = \bigcup_{\alpha \in I} U_\alpha.
	\]
	together with homeomorphisms $\psi_\alpha: U_\alpha \to \mathbb R^n$ is called an \textbf{atlas} for $M$. In order to make sense of $M$ in terms of an atlas, we define \textbf{transition maps} between different $U_\alpha$ by $\varphi_\beta \circ \varphi_{\alpha}^{-1}$.
	
	By using transition maps, we can transport data locally defined on $U_{\alpha}$ to other parts of $M$ by ``moving it across'' other $U_\beta$. This data often comes from the fiber bundles over $M$. This gives us an ability to ``glue together'' locally trivial bundles on the $U_\alpha$ to construct a globally nontrivial fiber bundle. For the fiber bundles of interest to us, there will be a group $G$ of automorphisms that acts on the fibers when comparing the data across different $U_\alpha$. We will later refer to $E$ as an \textbf{associated bundle} to $G$.
	We define this more precisely:
	\begin{defn}[Coordinate Bundle]
		A \textbf{coordinate bundle} consists of 
		\begin{itemize}
			\item A fiber bundle, defined as before
			\[
			\begin{tikzcd}
				F \arrow[r] & E  \arrow[d,"\pi"] \\ 
				& M
			\end{tikzcd}
			\]
			\item A group $G$, called the \textbf{structure group} of $E$ acting effectively on each fiber\footnote{A $G$-action is effective if only the identity element acts trivially i.e. $\forall g\in G \, \exists f \in F \mid gf \neq x$. The reason for this is that if $G$ did not act effectively, then elements that act trivially would give a normal subgroup $N$. Upon passing to the quotient we would get an effective action of $G/N$ on $F$.}
			\item A set of open coverings $\{ U_\alpha \}_{\alpha \in I}$ of $M$ with diffeomorphisms $\phi_\alpha: U_\alpha \times F \rightarrow \pi^{-1} (U_i)$ called \textbf{local trivializations} so that the following diagram commutes
			\[
			\begin{tikzcd}[row sep=2.5em]
			U_\alpha \times F \arrow[dr,swap,"p_1"] \arrow{rr}{\psi_\alpha} && \pi^{-1}(U_\alpha) \arrow{dl}{\pi} \\
			 & U_\alpha \\
			\end{tikzcd}
			\]
			\item For each $p \in U_\alpha \cap U_\beta$, $\psi_\beta^{-1} \psi_\alpha$ act continuously on the fiber $\pi^{-1}(p)$, coinciding the action of an element of $G$.
		\end{itemize}
		% diffeomorphism\footnote{This is a diffeomorphism in this case because we are considering a $C^\infty$ fiber bundle. If we were considering continuous, differentiable, or holomorphic fiber bundles this map would be continuous, differentiable, or holomorphic respectively.}
		
		% $\psi_\alpha$ captures the explicit isomorphism data between the fiber object $F$ and the fiber at a point $F_p$. $\psi_{\alpha, F_p} (f) = \psi_\alpha (p, x)$
	\end{defn}
		
	In gauge theory, $G$ is taken to be a \textbf{Lie group} called the \textbf{structure group} of $E$.
	\begin{defn}
		A Lie group is a group that is also a differentiable manifold so that the group operations of multiplication and inversion are compatible with the  differentiable structure. 
	\end{defn}
	A basic working knowledge of Lie theory is assumed, however we will go over relevant aspects of Lie groups in the following sections of this chapter.
	
	\begin{nb}
		In the above, we described $\varphi_\alpha$, $\tau_{\alpha \to \beta}$, and $\psi_\beta^{-1} \psi_\alpha$ as \emph{homeomorphisms}, which are morphisms in the category of topological spaces. If we wish to work in other categories, such as $C^r$-differentiable, smooth, analytic, or complex manifolds, then the transition functions are appropriately redefined to be functions that are $C^r$-differentiable, smooth, convergent Taylor series, or holomorphic respectively. 
		If we were working in the category of algebraic varieties, the corresponding maps we consider would have to be \emph{regular}.
	\end{nb}	
		%
		% From this we can define the vertical component of a point in the total space: $f_\alpha: E \rightarrow F$ by $f_\alpha = \psi^{-1}_{\alpha, \pi}$.
		
		At the fiber over each point, since we can identify $\psi^{-1}_{\beta, p} \circ \psi_{\alpha, p}$ with an element in $G$, we write $g_{\alpha, \beta}: U_{\alpha \beta} \rightarrow G$ to denote the $G$ action fiberwise on the overlap of the two bundles over $U_\alpha, U_\beta$. This translates data from one coordinate patch into the other.
		\begin{prop}
			$g_{\alpha \beta}$ satisfies 
			\begin{itemize}
				\item (identity) $g_{\alpha \alpha} = 1$
				\item (inversion) $g_{\alpha \beta} = g^{-1}_{\beta \alpha}$
				\item (cocycle condition) On $U_\alpha \cap U_\beta \cap U_\gamma$ $g_{\alpha \beta} g_{\beta \gamma} = g_{\alpha \gamma}$
			\end{itemize}
			\label{prop:cocycle}
		\end{prop}
		% One way to look at fiber bundles (c.f. \cite{lindenhovius2011}) is to define on the restriction of $E$ to each $U_\alpha$, functions $f_\alpha: U_\alpha \to F$ given by $f_\alpha(x) := p_2 p_1^{-1} (p)$
%
% 			Moreover, pick $x \in U_\alpha \cap U_\beta$ and $F_\alpha, F_\beta$ be the fibers over $x$ of $E$ as a bundle on $U_\alpha, U_\beta$ respectively.
% 			\begin{enumerate}
% 				\item $g_{\alpha \beta} F_\beta = F_\alpha$, that is $g_{\alpha \beta}$ gives the isomorphism to the the fiber corresponding to $U_\beta$ to the fiber corresponding to $U_\alpha$.
% 				\item $\psi_{\beta} (p, f) = \psi_{\alpha} (p, g_{\alpha \beta} f)$
% 			\end{enumerate}
%
%
% 		\begin{proof}
% 			These are all easy to check just by the definition of $g_{\alpha \beta}$ as a composition of the $\psi_\alpha$ and by invoking the cartesian properties of local trivialization.
% 		\end{proof}
		The equivalence class of a set of coordinate bundles on $M$ is the corresponding fiber bundle over $M$.
		
		Fiber bundles whose fibers are vector spaces are called \textbf{vector bundles}. The \textbf{rank} of a vector bundle is the dimension of the vector space fiber. A rank $n$ vector bundle over a field $\kk$ will have its structure group $G \subseteq \GL_n(\kk)$. Examples are the tangent/cotangent bundles of a manifold, and any tensor/symmetric/exterior powers thereof. We will see that we can view vector fields, $p$-forms, and many other interesting and physically-relevant objects as \textbf{sections} of fiber bundles, to be described in the later sections.
		
		\subsection{Morphisms and Extensions}
		The morphisms in the category of fiber bundles are called \textbf{bundle maps}:
		
		\begin{defn}[Bundle Map]
			For two fiber bundles $\pi: E \rightarrow M, \pi': E' \rightarrow M'$ a bundle map is a smooth map $\overline f: E \rightarrow E'$ that naturally induces a smooth map on the base spaces so that the following diagram commutes:
			\[
			\begin{tikzcd}
			E \arrow{r}{\overline f} \arrow{d}{\pi} & E' \arrow{d}{\pi'} \\
			M \arrow{r}{f} & M.
			\end{tikzcd}
			\]
		\end{defn}
		From this we obtain the way which we will identify two bundles as identical.
		\begin{defn}[Equivalence of fiber bundles]
			Two bundles are equivalent if there is a bundle map so that both $\overline f$ and $f$ are diffeomorphisms. 
		\end{defn}
		If we have a fiber bundle $\pi: E \rightarrow M$ and $\varphi: N \rightarrow M$ for another manifold $N$, then we can pull back $E$ to form a bundle over $N$
		\[
			\varphi^* E = \{(y,[f,p]) \in N \times E \mid \varphi(y) = p \}.
		\]
		We have projection on the second factor of $\varphi^* E$ as a map $g: \varphi^* E \rightarrow E$. 
		This is the \textbf{pullback bundle} $\varphi^* E$.
		\begin{defn}[Pullback Bundle]
			For a map $\varphi: N \rightarrow M$ and $E$ a fiber bundle over $M$ so that $\pi: E \rightarrow M$, we define the pullback bundle $\varphi^* E$ so that the following diagram commutes:
			\[
			\begin{tikzcd}
			\varphi^* E \arrow{r}{g} \arrow{d}{\pi'} & E \arrow{d}{\pi} \\
			N \arrow{r}{\varphi} & M.
			\end{tikzcd}
			\]
		\end{defn}
		Let us consider an example which will appear later in the context of studying a monopole placed at the origin of $\rr^3$.
		\begin{eg}
			Consider a vector bundle $E  \to \rr^3 \backslash \{0\}$. The pullback  gives rise to a vector bundle on $S^2$. This should be thought of as the restriction of $E$ to the sphere $S^2$.
		\end{eg}
		
		We can take products of fiber bundles as topological spaces in the obvious way to obtain a fiber bundle over $M \times M'$,
		\[
			E \times E' \xrightarrow{\pi \times \pi'} M \times M'.
		\]
		In the special case where $M = M'$ we can also define 
		\begin{defn}[Whitney Sum of Vector Bundles]
			For $E, E'$ vector bundles over $M$ with structure groups $G, G'$ respectively, we can define their sum as $E \oplus E'$ to be pullback bundle $E \times E'$ along the diagonal map $\Delta: M \rightarrow M \times M$.
			
		More explicitly, this is a fiber bundle over $M$ with $F \oplus F'$ fibered over every point. 
		The structure group of $E \oplus E'$ is the product $G \times G'$ of the structure groups of the original bundles and it acts diagonally on their sum.
		\[
			G^{E \oplus E'} = \left \{ \begin{pmatrix}
				g^E & 0 \\
				0 & g^{E'}
			\end{pmatrix} : g^E \in G, g^{E'} \in G' \right \}
		\]
		and the transition functions act diagonally in the same way. 
		\end{defn}
		Similarly, we can define arbitrary direct sums of bundles $E_1 \oplus \dots \oplus E_r$ recursively using the above definition.
		
		For some intuition about when fiber bundles are \emph{nontrivial}, consider the following theorem which we state without proof but refer to \cite{bott1982} chapter 3. Stated simply: taking the pullback of a bundle along a map is topologically invariant under homotopy of the map. 
		\begin{theorem}
			Let $\pi:E \rightarrow M$ be a fiber bundle over $M$ and consider maps $f, g$ from $N \rightarrow M$ so that $f, g$ are homotopic, then the pullback bundles are equivalent: $f^* E \cong g^* E$ over $N$.
		\end{theorem}
		An important fact is the following corollary of this theorem.
		\begin{cor}
			If $M$ is contractible, every fiber bundle $\pi: E \rightarrow M$ is topologically trivial\footnote{In the language of classifying spaces, $M$ being trivial implies there is only one homotopy class of map $M \to BG$, so that consequently the only fiber bundle over $M$ is the trivial one.}.
		\end{cor}
		\begin{proof}
			Let $f: pt \to M$ and $g: M \to pt$ be such that $f \circ g \sim id|_M$ and $g \circ f \sim id|_{pt}$. Then because pullback respects homotopy equivalence, we will have that $E \sim (f \circ g)^* E \sim f^* (g^*E)$ but $g^* E$ is the (necessarily trivial) bundle on a point, so this will pull back along $f$ to the trivial bundle along $f$.
		\end{proof}
		
		\subsection{Principal Bundles} % (fold)
		\label{sub:principal_bundles}
		

		
		We have seen that in general, the structure group of a fiber bundle acts effectively on the fibers. More strictly, when $G$ acts freely\footnote{A free $G$-action on $F$ is one where $\forall f \in F, gf = f \Rightarrow g = 1$ i.e. each element has only the identity fixing it. This is a more restrictive form of effective action.} and transitively\footnote{A transitive $G$-action on $F$ is one with a single $G$-orbit, i.e. any element can be taken to any other.} \emph{from the right}\footnote{The reason for defining this to be a \emph{right} action is so that it can commute with transition maps, which are taken to act from the \emph{left} \cite{stackoverflow1}.} on the fiber, we can identify $F$ with $G$. In this case, we get a \textbf{principal $G$-bundle}. This will be an object of central interest in what follows.
		
		\begin{obs}
			The fibers of a principal $G$-bundle are \emph{homeomorphic} to $G$
		\end{obs}
		\begin{proof}
			Let $P \to M$ be a principal $G$-bundle and pick a point $p \in M$. Take a point $f \in \pi^{-1}(p)$. We can construct a homeomorphism $\varphi: G \to \pi^{-1}(p)$ by sending $g \mapsto p g$. To prove that this is invertible, note that the action is transitive, so $\varphi$ is certainly surjective. Further, if $p g = p g'$ then $p = p g {g'}^{-1}$ so necessarily $g = g'$, and we have injectivity as a map between topological spaces.
		\end{proof}
		
		
		\emph{Topologically} each fiber $F$ of a principal $G$-bundle looks like $G$. Unlike $G$, however. $F$ need not have a canonical choice of identity element and consequently does not generically have canonical groups structure. Indeed, if it did then the bundle would necessarily have to be the trivial one $M \times G$. Such a space, that looks like $G$ after ``forgetting'' which point is the identity is called a \textbf{$G$-torsor}. 
		
		We give a an example for motivation:
		\begin{eg}[Frame Bundle]
			The fiber bundle of all \textbf{frames}, namely choices of bases in an $n$-dimensional space $V$ is a principal $\mathrm{GL}_n(V)$ bundle. Given a quadratic form $Q$ that defines a notion of orthonormality, the bundle of all orthogonal frames is a principal $\SO_n(V)$ bundle.
		\end{eg}
		The frame bundle is generally nontrivial. 
		
		\begin{eg}
			As another example, taking $G$ to be a discrete group and $\tilde X \to X$ be the universal cover of a topological space $X$, we get that $\tilde X$ is a principal $G$-bundle on $X$ with $G=\pi_1(X)$.
		\end{eg}
		
		Since $G$ acts transitively on the fiber, there is only one $G$ orbit and we can form the quotient $P/G$ in a well-defined way. We then have that $P/G$ is homeomorphic to $M$.
		% We state the following theorem (c.f. Chapter 9 of \cite{lee2003}).
	% 	\begin{theorem}
	% 		When $G$ is a compact Lie Group acting smoothly and freely on a manifold $M$, the orbit space $M/G$ is a topological manifold with dimension $\dim M - \dim G$ and a unique smooth structure so that $\pi: M \rightarrow M/G$ is a smooth submersion (differential is locally surjective).
	% 	\end{theorem}
	%
		% \begin{cor}
		% 	For a $G$-principal bundle $P \to M$ we get $\dim P = \dim M + \dim G$.
		% \end{cor}
		
		If $M,F$ are two manifolds and $G$ has an action $G \times F \rightarrow F$, then for an open cover $\{ U_\alpha \}$ of $M$ with a map $g_{\alpha \beta}: U_{\alpha}\cap U_{\beta} \to G$ satisfying the conditions of Proposition \ref{prop:cocycle} we can construct a fiber bundle by first building the set
		\[
			X = \bigcup_\alpha U_\alpha \times F
		\]
		and quotienting out by the relation
		\[
			(x, f) \in U_\alpha \times F \sim (x', f') \in U_\beta \times F \Longleftrightarrow x=x', f=g_{\alpha \beta}(x) f' .
		\]
		
		Then, $E = X/\sim$ is a fiber bundle over $M$. We can locally denote elements of $E$ by $[x,f]$ so that
		\[
			\pi(x,f) = x, ~ \psi_\alpha(x,f) = [x,f].
		\]
		
		\begin{prop}
			For a fiber bundle $\pi: E \rightarrow M$ with overlap functions $g_{\alpha \beta}: U_{\alpha \beta} \rightarrow G$ between charts, we can form a principal bundle $P$ so that 
			\[
				P = X/\sim, ~ X = \bigcup_\alpha U_\alpha \times G.
			\]
		\end{prop}
		In certain contexts that we will encounter later, the $g_{\alpha \beta}$ are referred to as \textbf{clutching functions}.		%
		% Note that there was no requirement here that $G$ be compact. \\
		
		\begin{eg}
			Take $M = \cp^1$ the Riemann sphere and consider constructing a $G$-bundle over it. The Riemann sphere can be decomposed as a union of two copies of $\cc$ with overlap exactly on the cylinder $\cc^{\times}$. On each copy of $\cc$ the $G$-bundle is trivializable since $\cc$ is contractible. A clutching function would be a map $\rho: \cc^\times \to G$, and this gives rise to a principal $G$-bundle on $M$. 
		\end{eg}
		
		This discussion leads naturally to the next subsection. 
		
		% subsection principal_bundles (end)
		
		\subsection{Associated Bundles}
		Take a principal bundle $P$ and let $F$ be a space with associated automorphism $\mathrm{Aut}(F)$ so that $\rho: G \to \mathrm{Aut}(F)$ is a \emph{faithful} representation. Then $g \cdot f$ is a well-defined faithful left $G$-action.
		\begin{defn}
			Given a principal bundle $\pi: P \to M$ and group action $\rho: G \to \mathrm{Aut}(F)$, the \textbf{associated bundle} is given by taking the product space $P \times F$ and forming the quotient space:
			\[
				(P \times F) / G
			\]
			given by identifying:
			\[
				(x g, f) \sim (x, \rho(g) f).
			\]
			This is the \textbf{fiber product} $P \times_{G, \rho} F$. The projection map:
			\[
				\pi': (P \times F) / G \to M
			\]
			is given by sending $(x, f)$ to $\pi(x)$ is well-defined since $\pi(x g) = \pi(x)$.
		\end{defn}
		Note that the (equivalence classes of) a coordinate bundles in section \ref{sub:definitions_and_examples} gives an associated bundle.
		
		
		% \begin{equation}
% 			g \cdot ([p, h], f) = ([p, hg], \rho(g)^{-1} f)
% 		\end{equation}
% 		This is a free action as well. Then if $G$ is compact (important) we have the orbit space
% 		\begin{equation}
% 			E_\rho = P(M,G) \times F/G
% 		\end{equation}
% 		is a manifold
%
% 		\begin{theorem}
% 			The space $E_\rho$ can be made into a fiber bundle over $M$ with fiber $F$ called the \textbf{associated fiber bundle} of $P(M,G)$.
% 		\end{theorem}
% 		\begin{proof}
% 			(Following \cite{lindenhovius2011})
% 			We make $P \times F$ into a bundle by defining the projection
% 			\begin{equation}
% 				\pi_\rho ([p, h], f) = p
% 			\end{equation}
% 			and trivializations $\psi_\alpha: U_\alpha \times F \rightarrow \pi^{-1}(U)\alpha$ by
% 			\begin{equation}
% 				(\psi_\rho)_\alpha (p, f) = ([p, s_\alpha (p)] , f)
% 			\end{equation}
% 			and inverse
% 			\begin{equation}
% 				(\psi_\rho)_\alpha^{-1} ([p, g], f) = [p, \rho(g) f]
% 			\end{equation}
% 		\end{proof}
		
		Two associated bundles that we'll care about are $P \times_{\mathrm{Ad}} G$ and $P \times_{\mathrm{ad}} \frak g$. The latter will be a vector bundle known as the \textbf{adjoint bundle}.
		
		Every fiber bundle with some structure group $G$ arises as an associated bundle to some principal $G$-bundle.
		Importantly, the study of equivalence classes of $G$-bundles can be equivalently cast as a study of certain associated bundles. 
		
		\subsection{Sections and Lifts}
		
		As mentioned before, any specific smooth vector field on a manifold $M$ can be viewed as a smooth map from $M$ to the the tangent bundle of $M$: $TM$. This motivates the notion of a \textbf{section} of a fiber bundle that associates to each base point $p\in M$ an element $f$ in the fiber $E_p$. Explicitly:
		\begin{defn}[Section of a Fiber Bundle]
			A \textbf{global section} of the fiber bundle $\pi: E \rightarrow M$ is a map $s: M \rightarrow E$ so that $\pi \circ s = \text{id}$. 
			
			When we have, $s: U \subseteq M \rightarrow E$, we call $s$ a \textbf{local section}. The set of global sections is denoted by $\Gamma(M, E)$. In different contexts, this may mean sections that are continuous, smooth, holomorphic, regular, etc. For smooth sections, this space is often denoted $\Gamma^\infty(M,E)$.
		\end{defn}
		
		
		\begin{eg}
			The set of all smooth $r$-forms on $M$ is $\Gamma^\infty(M, \Lambda^r (T^* M))$ on which the structure group $G$ of $T^*M$ acts on each component. % Note the different action of the structure group on different $r$-forms is exactly what makes the components of various $r$-forms ``$r$-times covariant''.
		\end{eg}
		% When the group is fibered over the manifold, then on the local cartesian structure, we can easily pick the section $p \mapsto [p,s(p)]$.
		
		\begin{prop}
			For a principal bundle $P$, any local trivialization $\psi: U \times G \rightarrow \pi^{-1} (U)$ defines a local section by $s: p \mapsto \psi(p, e)$ and conversely any local section defines a trivialization by $\psi(p,g) = s(p) g$
		\end{prop}
		
		% By using the language of sections, we can prove the existence of lifts. That is, for a principal bundle $P(M,G)$ over $M$, and a map $\varphi: M \to N$ we can get a principal bundle over $N$ by forming the projection $\varphi \circ \pi$.
		%
		% \textbf{FIX}
		% \begin{prop}
		% 	For a principal bundle $P(M,G)$ and $\varphi: M \rightarrow N$, then $\varphi$ is smooth iff $\varphi \circ \pi$ is smooth according to the following diagram.
		% 	\[
		% 	\begin{tikzcd}
		% 		P(M,G) \arrow{d}{\pi} \arrow{rd}{\varphi \circ \pi}\\
		% 		M \arrow{r}{\varphi} & N
		% 	\end{tikzcd}
		% 	\]
		% \end{prop}
		% \begin{proof}
		% 	If $\varphi$ is smooth, then $\varphi \circ \pi$ is a composition of smooth maps. On the other hand, if $\varphi \circ \pi$ is smooth, then for each point $p$ there is a coordinate neighborhood $U_\alpha$ on which we have trivial fiber structure. Take a local section $s_\alpha$ so that $\varphi \circ \pi \circ s = \varphi|_{U_\alpha}$.
		% \end{proof}
		%
		% \begin{prop}
		% 	For $P(M,G)$ principal and $\tilde \varphi: P(M,G) \rightarrow N$ a smooth $G$-invariant map so that
		% 	\begin{equation}
		% 		\tilde \varphi(x g) = \tilde \phi (x), ~ x \in P(M,G)
		% 	\end{equation}
		% 	then there is a unique map $\phi$ induced on the base space so that the following diagram commutes:
		% 	\[
		% 	\begin{tikzcd}
		% 		P(M,G) \arrow{d}{\pi} \arrow{rd}{\tilde \varphi}\\
		% 		M \arrow[r,dashed,"\varphi"] & N
		% 	\end{tikzcd}
		% 	\]
		% 	and is given by $\tilde \phi([x, g]) = \varphi(x)$. This is well-defined.
		% \end{prop}
		
		\section{Lie Theory} % (fold)
		\label{sec:lie_theory}
		
		% section lie_theory (end)
		
		Although standard knowledge on the definition of a Lie Group/Algebra is assumed, we will try to motivate the ideas in this field in a more geometric way than is often done. \\
		
		Consider a manifold $M$, and take $\text{Vect}(M)$ the space of all smooth vector fields on $M$. For a map $\varphi: M \rightarrow N$ we have a \textbf{pushforward} $\varphi_*: \text{Vect}(M) \rightarrow \text{Vect}(N)$ on vector fields given by
		\[
			[\varphi_* (v)] (f) = v (\varphi^* (f)).
		\]
		A smooth vector field $X$ on $M$ gives rise to \textbf{flows} $\gamma(t)$ that are solutions to the differential equation of motion
		\[
			\frac{d}{dt} f(\gamma(t)) = X f.
		\]
		Any ordinary differential equations has an interpretation as equations of motion along flows of vector fields in some space.  
		
		The motion along this flow is expressed as the exponential
		\[
			f(\gamma(t)) = e^{t X} f(p), ~ p = \gamma(0).
		\]
		
		Now consider two vector fields $X,Y$ on $M$. Let $Y$ flow along $X$ so we move along $X$ giving
		\[
			e^{tX} Y = Y(\gamma(t)) \in T_{\gamma(t)}M.
		\]
		Note that the reverse flow $e^{-t X}$ maps $T_{\gamma(t)} M \to T_{\gamma(0)}M = T_pM$, so acts by pushforward on $e^{tX} Y$ equivalent to:
		\[
			e^{tX} Y e^{-tX} \in T_p.
		\]
		We can compare this to $Y$ and take the local change by dividing through by $t$ as $t \to 0$, giving the Lie derivative
		\begin{equation}
			\mathcal L_X Y := \frac{e^{tX} Y e^{-tX} - Y}{t}.
		\end{equation}
		It is easy to check that this is in fact antisymmetric and gives rise to a bilinear form on $\mathrm{Vect}(M)$
		\begin{equation}
			[X,Y]:= L_X Y.
		\end{equation}
		A vector space endowed with such a bilinear form and satisfying the Jacobi identity is a \textbf{Lie algebra}.
		
		Most important is when $M$ itself has group structure, so is a Lie group, which we will denote by $G$. Then the vector fields on $G$ of course also form a Lie algebra, just by virtue of the manifold structure of $G$. 
		
		We state the following proposition without proof
		\begin{prop}\label{prop:pushforward}
			Let $\varphi: G_1 \rightarrow G_2$ be a homomorphism of Lie groups, then $\varphi_*: \mathrm{Vect}(G_1) \rightarrow \mathrm{Vect}(G_2)$ is a homomorphism of Lie algebras. 
		\end{prop}
		
		For a Lie group, group elements induce automorphisms on the manifold by left multiplication, denoted $L_g$ and by right multiplication $R_g$:
		\[
			\begin{aligned}
				R_g: G \rightarrow G, ~ g: h \mapsto gh\\
				L_g: G \rightarrow G, ~ g: h \mapsto hg.
			\end{aligned}
		\]
		 We have that each group element induces (by pushforward) a map between tangent spaces 
		\[
		 	\begin{aligned}
		 		(L_g)_*: T_h G \rightarrow T_{gh} G\\
				(R_g)_*: T_h G \rightarrow T_{hg} G
		 	\end{aligned}
		\]
		A vector field $X$ is called \textbf{left-invariant} if $(L_g)_* X(h) = X(gh)$. 
		By Proposition \ref{prop:pushforward}, we get that $(L_g)_* [X, Y] = [(L_g)_* X, (L_g)_* Y]$ so these left-invariant vector fields in fact form a Lie algebra for the group. Physically, this is the set of vector fields corresponding to the isometries of $G$.
		
		In local coordinates, the commutator can be written as:
		\[
			\begin{aligned}
				X = &X^\mu \partial_\mu, ~ Y = Y^\mu \partial_\mu\\
				[X,Y] = &(X^\nu \partial_\nu Y^\mu - Y^\nu \partial_\nu X^\mu) \partial_\mu.
			\end{aligned}
		\]
		Left-invariant vectors flow in a way that is consistent with the group action:
		\[
			(L_g)_* X(e) = X(g).
		\]
		The set of all left-invariant vector fields can be uniquely extracted from their value at the identity by this rule, and in fact for any vector $x \in T_e G$, there is a corresponding left-invariant vector field on $G$, $X|_g = (L_g)_* x$. Therefore the tangent space to the identity gives rise to a Lie algebra which we will call \emph{the} Lie algebra of $G$ and denote by $\frak g$. The Lie algebra of $G$ is finite dimensional when $G$ is and its dimension is equal to the dimension of $G$. We will also use the notation $\frak g = \mathrm{Lie}(G)$.
		
		
		Now because we define the Lie algebra as the ``tangent space to the identity'', it is worth asking ``how does the Lie algebra relate to the tangent space at a generic point, $g$, on the group?''. The idea is to bring that vector back to the identity using $G$ and see what it looks like. 
		
		This is accomplished by using the \textbf{Maurer-Cartan form} $\Theta$, which is a $\frak g$-valed 1-form on $G$ so that for $v \in T_g G$,
		\begin{equation}
			\Theta(g)(v) := (L_{g^{-1}})_* (v).
		\end{equation}
		% Note that this maps from $\mathrm{Vect}(G) \rightarrow \frak g$.
		
		For $G$ connected and simply connected, the ``inverse'' of the map $\mathrm{Lie}: G \to \frak g$ is a map $\frak g \to G$ suggestively denoted by $\exp$.
		\begin{prop}[Properties of $\exp$]
			For $G$ a compact and connected Lie group, with Lie algebra $\frak g$, we have a map $\exp : \frak g \rightarrow G$.
			\begin{enumerate}
				\item $[X,Y] = 0 \Leftrightarrow e^X e^Y = e^Y e^X$
				\item The map $t \rightarrow \exp(t X)$ is a homomorphism from $\mathbb R$ to $G$.
				\item If $G$ is connected then $\exp$ generates $G$ as a group, meaning all elements can be written as some product $\exp(X_1) \dots \exp(X_n)$ for $X_i \in \frak g$
				\item If $G$ is connected and compact then $\exp$ is surjective. It is almost never injective.
			\end{enumerate}
		\end{prop}
		
		\begin{eg}
			The Lie algebra associated to the Lie group $\mathrm U(n)$ of unitary matrices is $\frak u(n)$ of antihermitian matrices. This is the same as the Lie algebra for the group $\mathrm{SU}(n)$
		\end{eg}
		
		\begin{defn}[Adjoint Action on $G$]
			For each $g$ we can consider the homomorphism $\mathrm{Ad}_g: h \mapsto g h g^{-1}$ or $\mathrm{Ad}_g = L_g \circ R_{g^{-1}}$. This defines a representation
			\[
				\mathrm{Ad}: g \rightarrow \mathrm{Diff}(G)
			\]
		\end{defn}
		
		\begin{defn}[Adjoint Representation of $\frak g$]
			The pushforward of this action gives rise to the \textbf{adjoint representation} of the Lie group $\frak g$ by
			\[
				(\mathrm{Ad}_g)_* = (L_g \circ R_{g^{-1}})_* 
			\]
			From the product rule, this acts as $[g, -]$ at the identity. We denote this as
			\[
				\mathrm{ad}: \frak g \rightarrow \mathrm{End}~ \frak g
			\]
		\end{defn}
		
		The Jacobi identity ensures that $\mathrm{ad}$ is a homomorphism. If the center of $G$ is zero then $\mathrm{ad}$ is faithful and we have an embedding into $\mathrm{GL}(n)$. This is nice because it also shows that after a central extension, every Lie algebra can be embedded into $\mathrm{GL}(n)$, a weaker form of Ado's theorem (that all Lie algebras can be embedded into $\mathrm{GL}(n)$).
		
		Moreover the adjoint representation gives rise to a natural metric on $\gg$ called the \textbf{Killing Form} given by
		\begin{equation}
			\kappa (X, Y) := \mathrm{Tr}(\mathrm{ad}(X) \mathrm{ad}(Y)).
		\end{equation}
		
		\begin{prop}
			For $\frak g$ a semisimple Lie algebra, the above gives rise to a non-degenerate bilinear form. 
		\end{prop}
		For a proof see \cite{humphreys2012}.
		
		\section{The Group of Gauge Transformations}
		
		We use the ideas from the section on gauge transformation in \cite{lindenhovius2011} to build the following definition
		\begin{defn}[Gauge Transformation]
			Let $P$ be a principle bundle over $M$ with structure group $G$. A diffeomorphism $\Phi: P \to P$ is a \textbf{gauge transformation} if it satisfies the following two properties
			\begin{itemize}
				\item $\Phi$ preserves fibers so that the following diagram commutes
				\[
					\begin{tikzcd}
						P \arrow[rr,"\Phi"] \arrow[rd,"\pi"] & & P \arrow[ld,"\pi"]\\
						& M &
					\end{tikzcd}
				\]
				\item $\Phi$ commutes with the right $G$ action on $P$. 
			\end{itemize}
		\end{defn}
		Diffeomorphisms satisfying these conditions form a group referred to as the \textbf{group of gauge transformations}\footnote{Some authors may refer to this as the \emph{gauge group}. For us, the gauge group will be the $G$ we started with while this (much larger) group will be denoted $\mathcal G$.}. 
		
		As an illustration for intuition, a gauge choice on a trivial bundle over a space $M$ is just a map $\psi: M \to G$. A gauge transformation is then a section $g \in \Gamma^{\infty} (M, G)$ that acts by left action, transforming $\psi \to g \cdot \psi$.
		
		More generally for a principal $G$ bundle $P$ on a coordinate patch $U_\alpha$, gauge choices are maps from $U_\alpha \to P|_{U_\alpha}$, which can be interpreted the same way. 
		
		\section{Connections on Principal Bundles} % (fold)
		\label{sec:connections_on_principal_bundles}
		
		There are several different and equivalent ways to characterize the notion of a \textbf{connection} on a principal $G$-bundle. We will explore two prominent ones in this section. 
		
		\subsection{The Ehresman Connection}
		
		
		Take a $G$-principal bundle $\pi: P \rightarrow M$. The tangent space at any point $p \in P$ has a canonical subspace that is killed by $\pi_*$.
		\begin{defn}[Vertical Subspace]
			The \textbf{vertical subspace} $V_p P$ at a point $p$ of a fiber bundle is defined as $\ker \pi_*$. This can be thought of as the tangent space at $p$ restricted to the fiber over $\pi(p)$.
		\end{defn}
		
		Just as $\xi \in \frak g$ gives rise to a vector field $X_\xi$ on $G$, it also canonically gives rise to a vector field $\sigma(\xi)$ on $P$.
		\begin{defn}[\textbf{Fundamental Vector Field} of $\xi$]
			Let $\xi \in \frak g$ and consider $\exp(t \xi) \in G$ so that for $p \in P$ we get $c_p(t) = R_{\exp(t \xi)} p$ which depends smoothly on $p$. Note $c'_p(0) \in T_p P$ at each point.
			\[
			\sigma: \frak g \rightarrow \text{Vect}(P), ~ [\sigma(\xi)](p) \mapsto \left[ \frac{d}{dt} p e^{t \xi}\right]_{t=0}
			\]
		\end{defn}
		
		Note, by virtue of $\sigma(\xi)$ lying along the $G$-fiber. 
		\[
		\pi_* \circ \sigma(x) = \frac{d}{dt} (\pi \circ c_p(t))|_{t=0} = \frac{d}{dt} (p) = 0
		\]
		so $\sigma(x) \in V_p P$. 
		Since $P$ is a manifold of dimension $\dim M + \dim G$, $\pi_*: T_pP \rightarrow T_{\pi(p)}M$ has a kernel of dimension $\dim G = \dim \frak g$
		In fact:
		\begin{prop}
			$\sigma_p$ is a Lie algebra isomorphism between $\frak g$ and $V_pP$.
		\end{prop}
		\begin{proof}
		Since $G$ acts freely on principal bundles, $\sigma$ is injective, so in fact it must be an isomorphism.
		\end{proof}
	
		\begin{lemma}[Properties of $\sigma$]
			We get that $\sigma$ satisfies:
			\begin{enumerate}
				\item $[R_{g}]_* \sigma(x) = \sigma(\text{ad}_{g^{-1}} x)$,
				\item $[g_i]_* \sigma(x)|_p = g_i(p) x$.
			\end{enumerate}
		\end{lemma}
		\begin{proof}
			\begin{enumerate}
				\item We have
				\[
				\begin{aligned}
					\left[ R_{g} \right]_* [\sigma(x)](p)  &= \frac{d}{dt} (R_g p e^{tx}) \\
					& = \frac{d}{dt} p g \text{Ad}_{g^{-1}} e^{tx}\\ 
					& = \frac{d}{dt} p g \exp[ t (\text{ad}_{g^{-1}} x) ]\\
					& = [\sigma(\text{ad}_{g^{-1}} x)] (pg).
				\end{aligned}
				\]
				\item Secondly,
				\[
				\begin{aligned}
					\left[g_i\right]_* [\sigma(x)]|_p &= \frac{d}{dt} g_i p e^{t x}\\
										&= g_i(p) x.
				\end{aligned}	
				\]
			\end{enumerate}
		\end{proof}
	
		Now $\sigma$ respects the Lie algebra structure and forms a homomorphism from $\frak g$ to $\text{Vect}(P)$ so that in fact
		\begin{cor}\label{cor:verticalequiv}
			$(R_g)_* V_p = V_{pg}$: pushforward acts equivariantly on vertical subspaces.
		\end{cor}
		\begin{proof}
			Let $X(p) \in V_p$ pick $A \in \frak g$ so that the corresponding fundamental vector field is $\sigma(A) (p) = X(p)$. Then we just look at
			\[
				(R_g)_* \sigma(A) (p) = \sigma(\mathrm{ad}_{g^{-1}} A)(pg)
			\]
			which is vertical. It's easy to go back from $pg$ to $g$ as well by picking $A \in \frak g$ so that $X(pg) = \mathrm{ad}_{g^{-1}} A$.
		\end{proof}
	
		Now note:
		\[
		\begin{tikzcd}
			0 \arrow{r} & V_p P \arrow{r} & T_p P \arrow[r,"\pi_*"] & T_{\pi(p)}M \arrow{r} & 0
		\end{tikzcd}	
		\]
		An injection of $T_{\pi(p)} M$ into $T_p P$ to make the above sequence split is called a \textbf{horizontal subspace} at $p$ $H_pP$. 
		\begin{defn}[Horizontal Subspace]
			A horizontal subspace is a subspace $H_p P$ of $T_p P$ such that
			\[
				T_p P = V_p P \oplus H_p P.
			\]
		\end{defn}
		We'll abbreviate this by $H_p$ and the vertical subspace by $V_p$ when our principal bundle is unambiguous.
	 
		Crucially, there is \emph{no canonical choice of} $H_p$, reflecting the physical fact there is no ``god-given'' way to compare local gauges between different points. For a given gauge, a vector on $T_x M$ should lift to a vector on $T_p P$ for some $p$ corresponding to that gauge choice. The lift will lie in a horizontal subspace which will depend on the gauge choice in an infinitesimal neighborhood around $x$. A global choice of horizontal subspace gives rise to the following:
		\begin{defn}\label{def:ehresman}
		An \textbf{Ehresmann connection} is a choice of horizontal subspace at each point $p \in P$ so that
			\begin{enumerate}
				\item Any smooth vector field $X$ splits as a sum of two smooth vector fields: a \textbf{vertical field} $X_V$ and a \textbf{horizontal field} $X_H$ so that at each point $p \in P$ we have $X_V \in V_p$, $X_H \in H_p$. That is, the choice of $H_p$ varies smoothly.
				\item $G$ acts equivariantly on $H_{pg}$:
				\[
					H_{pg} = (R_{g})_* H_p.
				\]
			\end{enumerate}
		\end{defn}
	
		We will denote the collection of our choice of $H_p P$ by $HP$ and similarly define $VP$ to be the (always canonical) collection of vertical subspaces. We say any vector field can be split into a vector field $X^H \in HP$ and $X^V \in VP$.
	
		Naturally, for any choice of $HP$, we have a corresponding projection operator $\pi_H$ on vector fields $\pi_H: \mathrm{Vect}P \rightarrow HP$  and similarly $\pi_V = id - \pi_H$, both with corresponding equivariance conditions.
		
		Note that $1 - \pi_*$ acts on $T_p P$ as a projection operator onto the vertical subspace $V_p P$. A choice of horizontal subspace gives us an analogous projection operator $H$ acting on $T_p P$, mapping to the horizontal subspace. Moreover it is easy to check that (by the equivariance of the horizontal subspace), we must have
		\[
			[R_g]_* \circ H = H \circ [R_g]_*.
		\]
		
		Just as $\pi_*$ killed the vertical subspace, given a horizontal subspace, we would like to construct a similar operator that kills off the horizontal component and acts as a projection onto the vertical component. This role will be played by a \textbf{connection 1-form}

		\begin{defn}[Connection 1-form on Principal Bundle]\label{def:connection}
			A connection 1-form, $\omega$, is an element of $\Omega^1(P, \frak g)$ satisfying:
			\begin{itemize}
				\item $\omega \circ \sigma = id$, that is $\sigma \circ \omega$ is a projection onto $V_p$.
				\item $R_g^* \omega = \ad_{g^{-1}} \omega$.
			\end{itemize}
		\end{defn}
		The first condition says that, after identifying the vertical subspace with $\frak g$, $\omega$ acts trivially. The second condition is standard equivariance, since the right $\mathrm{ad}_G$-action on $\omega$ would exactly look like $g^{-1} \omega g$. 
	
		We now have the following equivalence:
		\begin{prop}
			A choice of Ehresman connection on $P$ is in one-to-one correspondence with the choice of a connection 1-form on $P$
		\end{prop}
		\begin{proof}
			Given a projection operator $H$ to the horizontal subspace satisfying the equivariance properties of \ref{def:ehresman}, $H_p P$, $1-H$ would be a projector onto the vertical subspace. Then $\sigma^{-1} (1- H)$ gives us a functional on $T_{p}$ valued in $\frak g$ that satisfies the properties of Definition \ref{def:connection}. This is our 1-form.
			
			Conversely, given a connection 1-form $\omega$, $1-\sigma \circ \omega$ gives us a projection onto a subspace trivially intersecting the vertical subspace. By the equivariance properties of $\omega$, this subspace satisfies the equivariance conditions in \ref{def:ehresman} and so we are done. 
		\end{proof}
		
	
		We thus have the following correspondence:
		\emph{
		\begin{center}
			\begin{tabular}{c c c c}
				\shortstack{Ehresman\\ Connections $HP$} & $\longleftrightarrow$ \shortstack{Horizontal\\Projection Operators $H$} & $\longleftrightarrow$ & \shortstack{Connection\\1-forms $\omega$}
			\end{tabular}
		\end{center}}
		Each of the above are smooth on $E$, and have appropriate equivariance conditions:
		\begin{itemize}
			\item $R_g H_p = H_{pg}$: Horizontal subspaces are $G$-equivariant,
			\item $[R_g]_* H = H [R_g]$: Horizontal projection commutes with $G$ action of changing gauge,
			\item $\omega(pg) = R_g^* \omega = g^{-1} \omega(p) g$: The 1-form is $G$-covariant.
		\end{itemize}

		Given a choice of gauge $s_\alpha$ on a given coordinate patch $U_\alpha$, we can define a $1$-form $A \in \Omega^1(M,\gg)$ by
		\begin{equation}
			A = s_\alpha^* \omega.
		\end{equation}
		This is the \textbf{connection 1-form on $M$}, and is the object that physicists are more used to working with in gauge theory.
		\begin{fact}
			The group of gauge transformations $\mathcal G$ acts on $A$ by
			\[
				A \to \ad_{g} A + g^{-1} \dd g.
			\]
			where $g$ is a function from $U_\alpha \to G$.
			Consequently, a connection $A$ that looks like $g^{-1} dg$ can be gauge transformed (by acting with $g^{-1}$) into the field $A=0$, and is consequently called \textbf{pure gauge}.
		\end{fact}
		

		\subsection{Differential Forms on Principal Bundles}

	

		\begin{defn}
			Given two $\gg$-valued differential forms $\alpha, \beta$ of ranks $p$ and $q$ respectively their wedge product is defined as
						\[
							(\alpha \wedge \beta)(v_1, \dots, v_{p+q}) = \frac{1}{(p+q)!} \sum_{\sigma \in S_n} \mathrm{sgn}(\sigma)\, [\alpha(v_{\sigma(1)}, \dots, v_{\sigma(p)}), \beta(v_{\sigma(p+1)}, \dots, v_{\sigma(p+q)})].
						\]
		\label{defn:wedgeforms}
		\end{defn}
		
		Take an associated $G$-bundle $E \to M$ given by $E = P \times_{\rho} F$ a $G$ action $\rho$. The 1-form $\omega$ gives us a way to act on forms $\alpha \in \Omega^p (M, F)$ that satisfy the equivariance condition $R_g^* \alpha = \rho(g^{-1}) \alpha$ by
		\[
			\dd_\omega \alpha = \dd \alpha + \rho(\omega) \wedge \alpha.
		\]
		This is the \textbf{exterior covariant derivative} associated to $\omega$. 
		In terms of $A$ this can be written as
		\begin{equation}
			\dd_A s := \dd s + \rho (A) \wedge s
		\end{equation}
		for a section $s$ of the associated bundle $E$.
		
		Given this, we define the \textbf{curvature form} $\Omega$ for a connection $\omega$ on a principal bundle $P$ to be
		\begin{equation}\label{curvature}
			\Omega := \dd_\omega \omega = d\omega + \omega \vee \omega.
		\end{equation}
		
		Further, a simple computation gives us the \textbf{Bianchi identity},
		\begin{equation}
			\dd_\omega \Omega = 0.
		\end{equation}
		
		Further, we have the \textbf{field-strength tensor} $F$ defined analogously to $A$ as
		\[
			F = s^* \Omega
		\]
		and satisfying the pulled-back Bianchi identity:
		\[
			\dd_A F = 0.
		\]
		
		The following lemmas, which we take from \cite{kobayashi1963}, are important in translating from a picture of $k$-forms on $P$ and $k$-forms on $M$.
		\begin{lemma}
			Let $\alpha$ be a $k$ form on a $G$-principal bundle $P \to M$. $\alpha$ will descend to a unique $k$-form $\overline \alpha$ on $M$ if the following are satisfied:
			\begin{itemize}
				\item $\alpha(v_1, \dots, v_k) = 0$ if $v_i$ is vertical for any $i$,
				\item $R_g^* \alpha = \alpha$, i.e. $\alpha(R_g v_1, \dots, R_g v_k)=\alpha(v_1, \dots, v_k)$.
			\end{itemize}
			In this case, we will have $\alpha = \pi^* \overline \alpha$.
			\label{lem:pushdown1}
		\end{lemma}
		\begin{proof}
			Let $\{\overline v_i\}_{i=1}^k$ be set of $k$ vectors in $T_p M$ and $\{v_i\}_{i=1}^k$ be a set of $k$ vectors in $T_x M$ for any $x \in \pi^{-1} (p)$ so that $\pi_* v_i = \overline v_i$. We define
			\[
				\overline \alpha(\overline v_1, \dots, \overline v_k) := \alpha(v_1, \dots, v_k)
			\]
			This is well-defined regardless of the choice of $\{v_i\}$ for given $\{\overline v_i\}$ since by hypothesis $\alpha$ is zero on the kernel of $\pi_*$. It is also independent of the choice of $x \in \pi^{-1}(p)$ by the hypothesis of $\alpha$'s invariance under right $G$ action.
		\end{proof}
		
		\begin{lemma}
			If $\alpha \in \Omega^1 (P, \frak g)$ descends to a form $\overline \alpha$ on $M$, then we have:
			\begin{equation}
				\dd_\omega \alpha = \dd \alpha
			\end{equation}
			\label{lem:pushdown2}
		\end{lemma}
		\begin{proof}
			This follows from the following manipulation:
			\[
				\begin{aligned}
					(\dd_\omega \alpha) (v_1, \dots, v_k) &= (\dd \alpha) (h v_1, \dots, h v_n)\\
					& = (\dd \pi^* \overline \alpha) (h v_1, \dots, h v_n)\\
					& = (\pi^* \dd \overline \alpha) (h v_1, \dots, h v_n)\\
					& = (\dd \overline \alpha) (\pi_* h v_1, \dots, \pi_* h v_n)\\
					& = (\dd \overline \alpha) (\pi_* v_1, \dots, \pi_* v_n)\\
					& = (\pi^* \dd \overline \alpha) (v_1, \dots, v_n)\\
					& = (\dd \alpha) (v_1, \dots, v_n).
				\end{aligned}
			\]
		\end{proof}

		\subsection{Holonomy} % (fold)
		\label{sub:holonomy}
		
		% subsection holonomy (end)
		
		A particularly important aspect of this thesis will be the action of Wilson loops when inserted into gauge theories. Wilson loops are defined in terms of what is known as the \textbf{holonomy} of a connection.
		
		The \textbf{concatenation} of two paths $\gamma_1, \gamma_2$ such that $\gamma_1(1) = \gamma_2(0)$ is the (piecewise smooth) curve given by
		\[
			\gamma'(t) := \begin{cases}
				\gamma_(2t)\text{ if } t \leq 1/2\\
				\gamma_(2t-1) \text{ if } 1/2 \leq t \leq 1.
			\end{cases}
		\]
		
		\begin{prop}
			Given a principal $G$-bundle $\pi:P\to M$, consider a smooth path $\gamma: [0, 1] \to M$. Given a point $p \in \pi^{-1}(\gamma(0))$, there is a unique lift $\tilde \gamma$ so that $\pi(\tilde \gamma) = \gamma$ and $\tilde \gamma'(t) \in H_{\tilde \gamma'(t)}P$. This is called the \textbf{horizontal lift} of $\gamma$
		\end{prop}
		\begin{proof}
			The result follows by noting that the condition that the lift be horizontal is a first order differential equation with unique specified initial conditions. By smoothness, there exists a unique solution.
		\end{proof}
		
		This can be generalized to piecewise smooth curves similarly.
		
		\begin{defn}
			The \textbf{holonomy group} for the connection $\omega$ at point $p \in P$, denoted $\mathrm{Hol}_p(\omega)$,  is the subgroup of $G$ consisting of elements that are holonomies around some loop $\gamma \subseteq M$.
			
			The \textbf{restricted holonomy group} $\mathrm{Hol}_p^0(\omega)$ is analogous, but considers only curves that are \emph{contractible}.
		\end{defn}
		Note that both of these are indeed subgroups, with multiplication of elements corresponding to the concatenation of the associated loops.
		
		A connection is called \textbf{irreducible} if the centralizer of the holonomy group in $G$ is precisely the center $Z(G)$.
		
		\begin{defn}
			A connection $\omega$ is called \textbf{flat} if $\Omega = 0$.
		\end{defn}
		It is easy to see that if a connection is flat then its holonomy around any contractible closed loop will be zero by Stokes' theorem. That is: the holonomy of a flat connection captures information about the topology of $M$.
		
		\section{Chern-Weil Theory}
		
		In physics, relevant quantities such as the action, the instanton number, and the gauge field Lagrangian are expressed in terms of polynomials of the field strength $F$. Chern-Weil theory is concerned with the study of polynomials of the curvature form $\Omega$ on the associated principal $G$-bundle that are invariant under the action of the gauge group. These can be related to the cohomology classes of $M$.
		
		\subsection{Symmetric Invariant Polynomials on $\frak g$}
		
		Consider $\gg$ as an affine algebraic variety ($\cong \cc^{\dim \gg}$), and consider the ring of functions $\cc [\gg]$. Since $G \lacts \gg$ by $\Ad_G$-action, we naturally have a $G$-action on this space of polynomials
		\[
			\cc [\gg] \racts G.
		\]
		Taking $f(x) \to f(\Ad_g x)$. Polynomials that are fixed by this action are called \textbf{invariant polynomials} on $\gg$, and are denoted by $\cc[\gg]^G$.
		
		\begin{eg}
			Take $\gg = \gl_n$. The following are invariant polynomials on $\gg$:
			\begin{itemize}
				\item $\tr x^n$ for any $n \in \zz^+$,
				\item $\det (x - \lambda \cdot 1)$ for any  $\lambda \in \cc$.
			\end{itemize}
			Invariance under $x \to gxg^{-1}$ follows from the cyclic properties of the trace in the first case and the fact that the determinant map is a homomorphism in the second case.
		\end{eg}
		
		\begin{defn}
			A polynomial $f$ on $\cc[\gg]$ is called \textbf{homogenous} of degree $k$ if $f(a x) = a^k f(x)$ for $x \in \gg, a \in \cc$.
		\end{defn}
		
		\begin{obs}
			A homogenous degree $k$ polynomial corresponds to an element of $\mathrm{Sym}^k (\gg^*)$: a $k$-linear symmetric functional $f: \prod_{i=1}^k \gg \to \cc$.
		\end{obs}
		
		We ask what it would mean to apply $f$ to the $\gg$-valued 2-form $\Omega$. By using Definition \ref{defn:wedgeforms} to construct a $k$-fold wedge products of 2-forms, we get a $2k$ form:
		\[
			f(\Omega)(v_1, \dots, v_{2k}) = \frac{1}{(2k)!} \sum_{\sigma \in S_n} \mathrm{sgn}(\sigma)\, f\left(\Omega(v_{\sigma(1)}, \dots, v_{\sigma(2)}), \dots ,\Omega(v_{\sigma(2k-1)}, \dots, v_{\sigma(2k)})\right).
		\]
		We now note that $f(\Omega)$ satisfies the requirements of Lemmas \ref{lem:pushdown1} and \ref{lem:pushdown2} so that 
		\[
			\dd f(\Omega) = \dd_\omega f(\Omega).
		\]
		Since $\dd_\omega$ acts as a graded derivation
		\[
			\dd_\omega (\alpha \wedge \beta) = (\dd_\omega \alpha) \wedge \beta + (-1)^{|\alpha|} \alpha \wedge (\dd_\omega \beta),
		\]
		and since $\dd_\omega \Omega = 0$ we get that $f(\Omega)$ is closed. Further, since $f(\Omega)$ descends to a $2k$-form $\overline{f(\Omega)}$, we get a closed $2k$ form on $M$, so that
		\begin{equation}
			[\overline{f(\Omega)}] \in H^{2k} (M).
		\end{equation}
		We formulate the following proposition:
		\begin{theorem}[Chern-Weil]
			Let $f$ be an invariant homogenous polynomial of degree $k$ on $\frak g$ and $\Omega$ be the curvature 2-form associated to some connection $\omega$ on a principle bundle $P$. Then $\overline{f(\Omega)}$ is a representative of a cocycle class in $H^{2k}(M)$ independent of the choice of connection.
		\label{thm:chern-weil}
		\end{theorem}
		\begin{proof}(Adopted from \cite{matthew2012})
			We have proved everything other than connection independence. For this, let $\omega_0, \omega_1$ be two different connection 1-forms on $P$. We can perform a homotopy and use the fact that cohomology is homotopy invariant. Consider $P$ as a principal $G$-bundle on $M \times [0, 1]$ and let $\omega':= t p^* \omega_0 + (1-t)  p^* \omega_1$ be the 1-form given by pulling back the appropriate combination of $\omega_0$ and $\omega_1$. Then using $\iota_t: M \to M \times [0,1]$ sending $p \to (p, t)$, $f(\Omega')$ can be pulled back from $M \times [0, 1]$ to a $2k$-form on $M$. Since $\iota_0$ and $\iota_1$ are homotopic:
			\[
				\iota_0^* \overline{f(\Omega')} \sim \iota_1^* \overline{f(\Omega')}
			\]
			must lie in the same cohomology class. This are easily seen to be equal to $\overline{f(\Omega_0)}$ and $\overline{f(\Omega_1)}$, respectively.
		\end{proof}

		We have the following corollary. 
		\begin{cor}
			For a manifold $M$, $\overline{f(\Omega_1)}$ is locally exact on each coordinate patch. The form $K$ so that $\dd K = \overline{f(\Omega_1)}$ on a given $U_\alpha$ is the \textbf{Chern-Simons} form.
		\end{cor}
		This form will play an important role in defining the instanton number for a principal $G$-bundle over $S^4$.
		
		\subsection{Chern Classes}
		
		Let $P$ be a principal $G$ bundle for $G$ real or complex and let $E$ be an associated \emph{complex} vector bundle on which $G$ acts nontrivially. For $G$ semisimple, this can be taken to be the adjoint bundle, but also for $G$ a classical, linear algebraic group, we can take the bundle to be associated to the defining representation. Let $n$ denote the rank of $E$.
		
		In either case, the curvature form $F \in \Omega^2(M, \gg)$ corresponding to a connection on $E$ gives rise to the following polynomial in $F$ that is easily seen to be symmetric-invariant:
		\begin{equation}
			c(F) := \det(1 - \frac{t F}{2\pi i})
		\end{equation}
		This polynomial is not homogenous, but rather splits into a sum of homogenous polynomials in even degree:
		\begin{equation}
			c(F) = 1 + t c_1(F) + t^2 c_2(F) + \dots = \sum_{k=1}^n t^k c_k(F)
		\end{equation}
		where $c_k \in \Omega^{2k}(M)$. Clearly $c_k(F) = 0$ if $2k > \dim M$.
		% where $c_i(F) \in H^{2i}(M)$ .
		
		By using simple matrix identities such as $\exp{\tr A} = \det \exp A$ one can arrive at a more explicit form of the first few of these polynomials
		\[
			c(F) = 1 + i \frac{\tr(F)}{2\pi} t + \frac{\tr(F \wedge F) - \tr(F) \wedge \tr(F)}{8\pi^2} t^2 + \dots + \frac{i \det F}{2\pi} t^n
		\]
		
		 By Theorem \ref{thm:chern-weil}, the cohomology classes $[c_i(F)]$ are independent of the connection used to define $F$. Consequently, we can define 
		 \begin{defn}[Chern class] \label{defn:chern}
		 	The \textbf{Chern classes} for the bundle $E$ are the cohomology classes in $H^*(M)$ associated with each $c_i(F)$. We write 
			\[
				c_i(E) := [c_i (F)].
			\]
			The \textbf{Chern numbers} for the bundle $E$ are given by
			\[
				c_i(E) := \int_{M} c_i(F)
			\]
			and are again independent of the connection. 
		 \end{defn}
		 
		
 		\begin{prop}
 			Let $E = \bigoplus_{j=1}^m E_j$. Then
 			\[
 				c(E) = c(E_1) \cdot \dots \cdot c(E_m)
 			\]
			where the product here is the cup product in cohomology.
 		\end{prop}
 		\begin{proof}
 			Because the gauge group acts as block matrices, the field strength tensor can be decomposed into blocks acting separately on each $E_j$ so that the determinant factors:
 			\[
 				\det\left(I - \frac{t F}{2\pi i}\right) = \det\left(I - \frac{t F_1}{2\pi i}\right) \wedge \dots \wedge \det \left(I - \frac{t F_m}{2\pi i}\right).
 			\]
			Thus, the associated Chern class is a cup product of the cohomology classes corresponding to each differential form in this wedge.
 		\end{proof}
		 